Optimizing Path ORAM for Cloud Storage Applications

### 2014-11-30 paper/paper.tex
Update paper.tex
z to Z

\begin{figure}
\begin{center}
  \includegraphics[width=6cm]{220.pdf}
  \caption{An example of a Path ORAM construction consisting of the binary tree (untrusted) and the stash and position map (trusted).}
  \label{fig:bintree}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8cm]{320.pdf}
\caption{Visual representation of how the User File System reads and writes files from and to Dropbox.}
\label{fig:userfilesys}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function showing the cumulative percentage of files of various sizes (KB).}
\label{fig:distfun}
\end{center}
\end{figure}

\subsection{Optimal Segment Size}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{520.pdf}
\caption{Sweep study comparing segment size with throughput (in MB/sec)}
\label{fig:segsize}
\end{center}
\end{figure}

@@

\subsection{Multi-Block Fetching}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{540.pdf}
\caption{Throughput (in MB/sec) of Path ORAM at different Multi-Block sizes.}
\label{fig:multiblock}
\end{center}
\end{figure}

@@

\label{sec:BlkPack}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4.3cm]{550.pdf}\includegraphics[width=4.3cm]{551.pdf}
\caption{Block Packing evaluations comparing tree size (in nodes) and throughput (in MB/sec)  with various file sizes (at segment size of 4 KB.)}
\label{fig:blockpack}
\end{center}
\end{figure}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.pdf}
\caption{Tree resizing demonstration charting size of tree over time.}
\label{fig:resizing}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=6cm]{220.pdf}
  \caption{Example of binary tree with blocks of data.}
  \label{fig:bintree}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8cm]{320.pdf}
\caption{User File System}
\label{fig:userfilesys}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function}
\label{fig:distfun}
\end{center}
\end{figure}

\subsection{Optimal Segment Size}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{520.pdf}
\caption{Segment Size Sweep Study}
\label{fig:segsize}
\end{center}
\end{figure}

@@

\subsection{Multi-Block Fetching}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{540.pdf}
\caption{Multi-Block Evaluation}
\label{fig:multiblock}
\end{center}
\end{figure}

@@

\label{sec:BlkPack}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4.3cm]{550.pdf}\includegraphics[width=4.3cm]{551.pdf}
\caption{Block Packing Evaluations}
\label{fig:blockpack}
\end{center}
\end{figure}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.pdf}
\caption{Tree Resizing Demonstration}
\label{fig:resizing}
\end{center}
\end{figure}
